Structural Divergence Analysis

### 2017-04-23 analysis-structure-core.Rmd
bibliografíapaper, varios r0 y dinámica

```{r set-my-colors}
# set my colors
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```

@@

```{r set-file-names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

## profiles to compare
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
```

@@

## strong
dri2.strong = read.csv(dri2.strong.fname, header = T)[, indexes.core]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
```

@@

```{r mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

@@

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(mean z.RSD)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

@@

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "mut")
d.strong = subset(d, dataset == "mut+sel")

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)

cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")

@@

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "mut.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "exp.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.strong$mean.z.RSD, 
     xlab = "mut.mean.z.RSD", 
     ylab = "strong.mean.z.RSD", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```
### Distance to the active site

@@

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CA[indexes.core], xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM[indexes.core], xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CA[indexes.core])
r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM[indexes.core])

cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

@@

>>>>

```{r set-my-colors}
# set my colors
myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "no-selection", "medium", "selection")
```

@@

```{r set-file-names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
sum.inv.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_sum.inv.da.CM.ca.csv", sep = ""))

## profiles to compare
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
sim.data.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
```

@@

## medium
dri2.medium = read.csv(dri2.medium.fname, header = T)[, indexes.core]
rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
```

@@

```{r mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))

@@

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_point() +
    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(<z.RSD>)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "no-selection")
p.facet %+% subset(d, dataset == "selection") 
p.facet

@@

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

@@

# calculate cors
r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)

cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
```

### Comparison between profiles

```{r comparisons-between-profiles}

@@

plot(x = d.exp$mean.z.RSD, 
     y = d.mut$mean.z.RSD, 
     xlab = "<z.RSD> experimental", 
     ylab = "<z.RSD> no-selection", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
abline(0, 1)

plot(x = d.exp$mean.z.RSD, 
     y = d.medium$mean.z.RSD, 
     xlab = "<z.RSD> experimental", 
     ylab = "<z.RSD> selection", 
     xlim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))),
     ylim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))))
points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)

plot(x = d.mut$mean.z.RSD, 
     y = d.medium$mean.z.RSD, 
     xlab = "<z.RSD> no-selection", 
     ylab = "<z.RSD> selection", 
     xlim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))),
     ylim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))))
points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
abline(0, 1)
```
### Distance to the active site

@@

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites])
r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites])

cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> no-selection) vs min.da.CA", "(<z.RSD> experimental - <z.RSD> no-selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites])
r.min.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites])

cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> selection) vs min.da.CA", "(<z.RSD> experimental - <z.RSD> selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

@@

```{r comparison-sum.inv.da}

# comparison of means.z.scores with the sum.inv distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")

## calculate correlations between profiles
r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites])
r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites])

cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> no-selection) vs sum.inv.da.CA", "(<z.RSD> experimental - <z.RSD> no-selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")

# comparison of means.z.scores with the sum.inv distance to the functional sites
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")

## calculate correlations between profiles
r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites])
r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites])

cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> selection) vs sum.inv.da.CA", "(<z.RSD> experimental - <z.RSD> selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")
```

```{r correlation-da-CN} 
## CN core
CN = CN[indexes.core]

## calculate correlations between profiles
r.min.da.CA.CN = cor(CN[-active.sites], m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites])
r.min.da.CM.CN = cor(CN[-active.sites], m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites])

cor.df = data.frame("comparison" = c("CN vs min.da.CA", "CN vs min.da.CM"), "R" = c(r.min.da.CA.CN, r.min.da.CM.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the minimal distance to the active site")

## calculate correlations between profiles
r.sum.inv.da.CA.CN = cor(CN[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites])
r.sum.inv.da.CM.CN = cor(CN[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites])

cor.df = data.frame("comparison" = c("CN vs sum.inv.da.CA", "CN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.CN, r.sum.inv.da.CM.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the sum.inv distance to the active site")
```

### Sequence comparison

In this section we compare theoretical sequence divergence profiles with sequence scores obtained from ConsurfDB. To obtain theoretical profiles, for each selection regimen, we calculated the number of times we had mutated each site and divided this number by the number of times we had tried a mutation at the site.

```{r sequence-profiles-comparison}
# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE[indexes.core]

# read simulated data
## no sel
sim.data.mut = read.csv(sim.data.mut.fname)
mut.site.mut = sim.data.mut$site
accept.mut = sim.data.mut$accept

## medium sel
sim.data.medium.sel = read.csv(sim.data.medium.sel.fname)
mut.site.medium.sel = sim.data.medium.sel$site
accept.medium.sel = sim.data.medium.sel$accept

# calculate p.accept of simulated data
p.accept.mut = c()
p.accept.medium.sel = c()

if (data.dir == "OUT/out_subset_CM_ANM") {
  mut.site.mut = mut.site.mut - n.sites
  mut.site.medium.sel = mut.site.medium.sel - n.sites
}

# core n.sites

for (i in (1:n.sites)) {
  accept.mut.i = accept.mut[which(mut.site.mut == i)]
  p.accept.mut.i = mean(accept.mut.i)
  p.accept.mut[i] = p.accept.mut.i

  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
  p.accept.medium.sel.i = mean(accept.medium.sel.i)
  p.accept.medium.sel[i] = p.accept.medium.sel.i
}
p.accept.mut = p.accept.mut[indexes.core]
p.accept.medium.sel = p.accept.medium.sel[indexes.core]

# compare exp vs no sel profiles
## plot
par(pty = "s")

plot(x = p.accept.mut, y = CN, xlab = "log(paccept no-selection)")
plot(x = p.accept.mut, y = score, xlab = "log(paccept no-selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.mut.CN = cor(log(p.accept.mut), CN)
r.p.accept.mut.score = cor(log(p.accept.mut), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")

# compare exp vs medium sel profiles
## plot
par(pty = "s")

plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
plot(x = score, y = CN)

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")

```
